\documentclass[12pt, notitlepage]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex

\usepackage{hyperref}
		
%SetFonts

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tgbonum}

%SetFonts

\title{
	\textbf{
		BIOL 4100-029
	} \\
	\large Undergraduate Research \\
	\large Spring 2025
}

\date{\vspace{-5ex}}

\begin{document}

{\fontfamily{phv}\selectfont %select helvetica (code = phv)

\maketitle

\section{List of Readings}

\textbf{Week of January 22, 2025}
\begin{itemize}
    \item No reading, first meeting
\end{itemize}

\textbf{Week of January 29, 2025}

\begin{itemize}
    \item Chapin III, FS. 2003. Effects of plant traits on ecosystem and regional processes: a conceptual framework for predicting the consequences of global change. \textit{Annals of Botany} 91: 455-463. \href{https://academic.oup.com/aob/article-abstract/91/4/455/213070?redirectedFrom=fulltext}{Link to paper here}.
\end{itemize}

\textbf{Week of February 05, 2025}

\begin{itemize}
    \item Long SP, Bernacchi CJ. 2003. Gas exchange measurements: what can they tell us about the underlying limitations to photosynthesis? Procedures and sources of error. \textit{Journal of Experimental Botany} 54: 2393-2401. \href{https://academic.oup.com/jxb/article/54/392/2393/621914}{Link to paper here}.
    \item Busch FA, Ainsworth EA, Amtmann A, Cavanagh AP, Driever SM, Ferguson JN, Kromdijk J, Lawson T, Leakey ADB, Matthews JSA, Meacham-Hensold K, Vath RL, Vialet-Chabrand S, Walker BJ, Papanatsiou M. 2024. A guide to photosynthetic gas exchange measurements: fundamental principles, best practice, and potential pitfalls. \textit{Plant, Cell and Environment} 47: 3344-3364. \href{https://onlinelibrary.wiley.com/doi/full/10.1111/pce.14815}{Link to paper here}.
\end{itemize}

\textbf{Week of February 12, 2025}
\begin{itemize}
    \item Ainsworth EA, Long SP. 2005. What have we learned from 15 years of free-air CO$_2$ enrichment (FACE)? A meta-analytic review of the responses of photosynthesis, canopy properties and plant production to rising CO$_2$. \textit{New Phytologist} 165: 351–372. \href{https://nph.onlinelibrary.wiley.com/doi/10.1111/j.1469-8137.2004.01224.x}{Link to paper here}.
\end{itemize}
\newpage
\textbf{Week of February 19, 2025}
\begin{itemize}
    \item Yamori W, Hikosaka K, Way DA. 2014. Temperature response of photosynthesis in C$_3$, C$_4$, and CAM plants: temperature acclimation and temperature adaptation. \textit{Photosynthesis Research} 119: 101–117. \href{https://link.springer.com/article/10.1007/s11120-013-9874-6}{Link to paper here}.
\end{itemize}

\textbf{Week of February 26, 2025}
\begin{itemize}
    \item Liang X, Zhang T, Lu X, Ellsworth DS, BassiriRad H, You C, Wang D, He P, Deng Q, Liu H, et al. 2020. Global response patterns of plant photosynthesis to nitrogen addition: A meta‐analysis. \textit{Global Change Biology} 26: 3585–3600. \href{https://onlinelibrary.wiley.com/doi/full/10.1111/gcb.15071}{Link to paper here}.
\end{itemize}

\textbf{Week of March 05, 2025}
\begin{itemize}
    \item Yue K, Fornara DA, Yang W, Peng Y, Peng C, Liu Z, Wu F. 2017. Influence of multiple global change drivers on terrestrial carbon storage: additive effects are common. \textit{Ecology Letters} 20: 663-672. \href{https://onlinelibrary.wiley.com/doi/full/10.1111/ele.12767}{Link to paper here}.
\end{itemize}

\textbf{Week of March 12, 2025}
\begin{itemize}
    \item Phillips RP, Brzostek ER, Midgley MG. 2013. The mycorrhizal-associated nutrient economy: a new framework for predicting carbon-nutrient couplings in temperate forests. \textit{New Phytologist} 199: 41–51. \href{https://nph.onlinelibrary.wiley.com/doi/full/10.1111/nph.12221}{Link to paper here}.
\end{itemize}

\textbf{Week of March 19, 2025}
\begin{itemize}
    \item No reading, Spring Break
\end{itemize}

\textbf{Week of March 26, 2025}
\begin{itemize}
    \item Terrer C, Vicca S, Stocker BD, Hungate BA, Phillips RP, Reich PB, Finzi AC, Prentice IC. 2018. Ecosystem responses to elevated CO$_2$ governed by plant–soil interactions and the cost of nitrogen acquisition. \textit{New Phytologist} 217: 507–522. \href{https://nph.onlinelibrary.wiley.com/doi/full/10.1111/nph.14872}{Link to paper here}.
\end{itemize}

\textbf{Weeks of April 02, April 09, and April 16, 2025}
\begin{itemize}
    \item No reading, work on proposal
\end{itemize}

\textbf{Weeks of April 23 and April 30, 2025}
\begin{itemize}
    \item No reading, proposal presentations
\end{itemize}

} %end font selection

\end{document} 